---
title: "Juvenile Barau's petrels in the EEZ of Seychelles"
author: "CCJ"
date: "11/10/2021"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float: true
---

```{r setup, include=FALSE}
library(sf)
library(mapview)
library(lubridate)
library(leafpop)
library(leaflet)
library(knitr)

# --------- #
# ZEE data #
# ------- #

# Worldwide

ZEE <- st_read('C:/Users/ccjuhasz/Downloads/EEZ_land_union_v3_202003/EEZ_Land_v3_202030.shp')
# Seychelles
terr <- unique(ZEE$TERRITORY1)
terr <- terr[order(terr)]
ZEE_Seych <- ZEE[ZEE$TERRITORY1 == 'Seychelles',]
# ------------------------------------------------------------------ #
#### Loading and treatment of data 2 - RAW cleaned localisations ####
# ---------------------------------------------------------------- #
argos <- read.table("C:/Users/ccjuhasz/Desktop/SMAC/Projet_publi/X-PTEBAR_argos_JUV/DATA/PTEBAR_JUV_Pinet_data_CLEANED.txt",
                    h = T,
                    sep = '\t',
                    dec = '.')
names(argos)[1] <- 'PTT'

# ---- Date class
argos$Date <- as.POSIXct(argos$Date,
                         format = "%Y-%m-%d %H:%M") # Date format
argos$deploy <- as.POSIXct(argos$deploy,
                           format = "%Y-%m-%d %H:%M") # Date format

# Conversion in sf Spatial Object
projLatLon <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
# UTM 43S corresponding to the center of the Indian ocean
# UTM 43 => 32743 
projUTM <- '+init=epsg:32743'

# Non projected spatial object
argos.sf <- st_as_sf(argos,
                     coords = c('Longitude', 'Latitude'),
                     crs = projLatLon)
# Projected spatial object
argos.sf.UTM <- st_transform(argos.sf,
                             crs = 32743)

# Find points in ZEE polygons
birds_in_ZEE <- st_join(argos.sf,
                        ZEE,
                        join = st_within)

# Birds in Seychelles ZEE
birds_Seych <- birds_in_ZEE[birds_in_ZEE$TERRITORY1 == 'Seychelles',]
birds_Seych <- birds_Seych[!is.na(birds_Seych$PTT),]
table(birds_Seych$PTT, useNA = 'always')

birds_Seych$PTT_fact <- as.factor(birds_Seych$PTT)

birds_Seych$popup_info <- paste0("<b>PTT</b> ",
                                 birds_Seych$PTT,
                                 "<br/>",
                                 "<b>Relocation date</b>",
                                 birds_Seych$Date,
                                 "<br/>")

# Summary of juvenile PTEBAR in the Seychelles ZEE

birds_Seych_list <- split(birds_Seych, birds_Seych$PTT)

sum_juv_Seych <- lapply(birds_Seych_list, function(x){
  
  ID <- unique(x$PTT)
  species <- 'PTEBAR'
  status <- 'JUV'
  device <- 'ARGOS'
  
  y <- year(unique(x$deploy))
  min.d <- min(x$Date)
  max.d <- max(x$Date)
  
  r <- c(ID = as.character(ID), species = species, status = status, device = device, year = y, input = as.character(min.d), output = as.character(max.d))

}) 
sum_juv_Seych_df <- as.data.frame(do.call('rbind', sum_juv_Seych))
sum_juv_Seych_df$input <- date(sum_juv_Seych_df$input)
sum_juv_Seych_df$output <- date(sum_juv_Seych_df$output)
```
# Overview  
  
Juvenile PTEBAR get through:  
* Amsterdam and Saint Paul Islands  
* Australia  
* Chagos Archipelago  
* Christmas Island  
* Cocos Islands  
* Comores  
* Glorioso Islands  
* Ile Tromelin  
* India  
* Indonesia  
* Madagascar  
* Maldives  
* Mayotte  
* Republic of Mauritius  
* Réunion  
* Seychelles  
* Sri Lanka  
* Tanzania  
  
# Summary of presences in the EEZ of Seychelles 
  
```{r, echo = F}
kable(sum_juv_Seych_df,
      row.names = F)
```
  
**ID**: Unique ID of individual  
**species**: PTEBAR is for *Pterodroma baraui*  
**status**: JUV is for juvenile  
**device**: system allowing the localisations  
**year**: year of deployment  
**input**: date of the first presence in the zone  
**output**: date of the last presence in the zone  
  
# Map illustrating the juvenile distribution  
  
*Please, try to click on points or on the 'multi-layer' icon*  
  
```{r, echo = F}
mapview(birds_Seych[, c(41, 40, 2, 6)],
        zcol = 'PTT_fact',
        # popup = popupTable(birds_Seych[, c(41, 40, 2, 6, 42)],
        #                    zcol = 'popup_info',
        #                    feature.id = FALSE,
        #                    row.numbers = FALSE,
        #                    className = 'mapview-popup'),
        # popup = birds_Seych$popup_info,
        # popup = popupTable(birds_Seych,
        #                    zcol = 'popup_info'),
        burst = TRUE,
        legend = F) + mapview(ZEE_Seych,
                             col.regions = 'darkgrey',
                             popup = F,
                             layer.name = 'Seychelles_EEZ')
```
  
**PTT_fact**: unique ID of individual  
**Date**: date of the relocation  
**deploy**: date of the device deployment